OSF management

### 2022-06-28 scripts/r/00_manage_osf.Rmd

Ugly code to do the job quickly. Need a-fixing.

@@

>>>>

@@

# Upload reviews.

```{r upload-analytic-responses}
osf_teams <- osf_retrieve_node("n3fyd")
# Warning, takes a minute
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)

reviews_csvs <- list.files("./data/peer_review/msa_reviews/")

teams <- str_remove(reviews_csvs, "\\.csv")

for (team in 1:length(teams)) {
  file_path <- glue("data/peer_review/msa_reviews/{teams[team]}.csv")
  osf_upload(teams_comps[which(teams_comps$name == teams[team]),], path = file_path, verbose = T, conflicts = "overwrite")
}
```

```{r delete-reviews}
for (team in teams) {
  file_name <- glue("{team}.csv")
  file_id <- osf_ls_files(teams_comps[which(teams_comps$name == team),], pattern = ".csv")
  if (nrow(file_id) > 0) {
    for (file in 1:nrow(file_id)) {
      if (file_id$name[file] %in% teams_files) {
        osf_rm(file_id[file,], check = FALSE)
      }
    }
  }
}
```
